A Case Study in Preserving a\\High Energy Physics Application

### 2014-03-20 paper.tex
remove completely in section 6

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the
complete environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems mentioned in~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files:    & 1632         & 15642\\ 
\hline
    Empty Files:    & 14273        & 263\\
\hline
    Directories:    & 1549         & 1549\\ 
\hline
    Symbolic Links: & 4614         & 4614 \\
\hline
    \bf Total Size: & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

Regardless, we demonstrate that the application runs correctly in a completely different environment.
%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.

>>>>

In a very abstract sense, reproducing a computation is trivial.
Assuming a computation is deterministic, one must simply
preserve all of the inputs to a computation, then re-run
the same code in an equivalent environment, and the same result
will be produced.  For a small custom application on a modest
amount of data, this could be accomplished by capturing the
complete environment,
data, and software within a single virtual machine image,
and then depositing the virtual
it into a curated environment.  The publication could
then simply refer to the identifier of the image, which the
interested reader can obtain and re-use. This approach has
been used to some success with systems~\cite{castagne2013consider}.
\footnote{Of course, we are glossing over the problem that hardware
architectures and virtual machines also change, so one must also
preserve the VMM software necessary to run the image.  The VMM itself
depends on a software environment which must also be preserved.
A long-term preservation system might end up running a whole
stack of nested virtual machines in order to provide the desired
environment! }

@@

\begin{table}
    \centering
    \begin{tabular}{|r|r|r|}
\hline
                    & \bf Shallow Copy & \bf Medium Copy\\
\hline
    Whole Files    & 1632         & 15642\\ 
\hline
    Empty Files    & 14273        & 263\\
\hline
    Directories    & 1549         & 1549\\ 
\hline
    Symbolic Links & 4614         & 4614 \\
\hline
    \bf Total Size & \bf 21GB     & \bf 28GB \\ 
\hline
    \end{tabular}
    \caption{Package Information}
    \label{table:package-info}
\end{table}

@@

Regardless, we demonstrate that the application can be repeated with the help of the reduced package on one different machine with the required hardware architecture and OS distribution version.
%*****hmeng-doubt:Another reason for the packaging utility is that not all the data and software generated by the second version script is used during the the actual data analysis. The packaging utility can help us find out the optimal subset of data and software involved in one actual data analysis. 
%*****hmeng-doubt: this point is not the motivation. but one achievement comes together. out of imagination.
